---
title: "p8105_hw1_jh4323.Rmd"
author: Jialiang hua
output: github_document
---

This is my first homework for P8105!

## Problem 1

### 1.1 Create a data frame according to the requirement

```{r prob1_df}
library(tidyverse)
set.seed(1)

problem1_df <- tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_char = c("James", "Linda", "Jerry", "Jason", "Mary", 
               "Michael", "Sarah", "David", "Betty", "Joseph"),
  vec_factor = factor(c("poor", "fair", "good", "fair", "poor", 
                        "poor", "good", "good", "fair", "good"))
)
```

### 1.2 Try to take the mean of each variable in the data frame

```{r take_mean}
mean(pull(problem1_df, vec_numeric))
mean(pull(problem1_df, vec_logical))
mean(pull(problem1_df, vec_char))
mean(pull(problem1_df, vec_factor))
```

The mean of the numeric vector and the logical vector can be taken 
from the data frame. However, it doesn't work for the character vector 
and the factor vector.

### 1.3 Convert to numeric

```{r convert_to_numeric, eval = FALSE}
as.numeric(FALSE)
as.numeric(TRUE)
as.numeric("James")
as.numeric(factor(c("male", "female", "female")))
```

The `as.numeric` function can successfully convert numeric and logical vector
to numbers. However, it can not convert character vector to numbers. In
particular, as.numeric applied to a factor is meaningless, and may happen 
by implicit coercion. This explains what happened when I try to take the mean.

## Problem 2

### 2.1 Load the `penguins` dataset

```{r}
data("penguins", package = "palmerpenguins")
```

### 2.2 Describe the dataset

The data in this dataset includes `r names(penguins)` important variables.
  
  Species contains `r levels(pull(penguins, species))`.  
  Island contains `r levels(pull(penguins, island))`.  
  Bill length range is (`r range(pull(penguins, bill_length_mm), na.rm =     TRUE)`).  
  Bill depth range is (`r range(pull(penguins, bill_depth_mm), na.rm = TRUE)`).  
  Body mass range is (`r range(pull(penguins, body_mass_g), na.rm = TRUE)`).  
  Sex includes `r levels(pull(penguins, sex))`.  
  Year range is (`r range(pull(penguins,year), na.rm = TRUE)`).  
  The size of the dataset is `r nrow(penguins)` rows and `r ncol(penguins)` columns.  
  The mean of flipper length is `r mean(pull(penguins, flipper_length_mm) , na.rm = TRUE)`.
  
### 2.3 Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x)

```{r scatter_plot}
library(ggplot2)
set.seed(1)

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

ggsave("penguins_scatterplot.pdf", height = 6, width = 6)
```



  
